### 2018-06-18 paper/7-related.tex
Add authors, minor changes
Fix paper build
Work on S3
Work on S5

\item \CloudBuild~\cite{esfahani2016cloudbuild}
differs from \Bazel by allowing non-determinism~\S\ref{sec-non-determinism}, thus more closely modelling
our original definition of \Bazel from \S\ref{sec-implementation-bazel}.

\item \Nix~\cite{dolstra2004nix} has coarse-grained dependencies, with precise
hashing of dependencies and downloading of precomputed build products. When
combined with \cmd{import-from-derivation}, \Nix can also be considered monadic,
making it similar to Cloud \Shake from~\S\ref{sec-implementation-cloud-shake}.
However, \Nix is not intended as a build system, and the coarse grained nature
(packages, not individual files) makes it targeted to a different purpose.
% John Ericson suggested in a blog comment that nix may be somewhat monadic, see:
% \url{https://blogs.ncl.ac.uk/andreymokhov/cloud-and-dynamic-builds/\#comment-1849}.

@@

\begin{minted}[xleftmargin=10pt]{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}

Provided we instantiate \hs{p} to something like
\hs{k}~\hs{->}~\hs{f}~\hs{v}~--~which many of the actual instances in that paper
do. The properties of such optics are well studied, and the functions like
\hs{dependencies} are very much based on observations from that field of work.
Alas, we have been unable to remove the \hs{Maybe} used to encode whether a file
is an input, without complicating other aspects of our definition. Furthermore,
the \hs{Build} operation lacks any further such symmetry.

>>>>

\item \CloudBuild~\cite{esfahani2016cloudbuild}
differs from \Bazel by allowing non-determinism~\S\ref{sec-non-determinism}, thus more closely modelling
our original definition of \Bazel from \S\ref{sec-implementation-bazel-cloud-shake}.

\item \Nix~\cite{dolstra2004nix} has coarse-grained dependencies, with precise
hashing of dependencies and downloading of precomputed build products. When
combined with \cmd{import-from-derivation}, \Nix can also be considered monadic,
making it similar to \Cloud \Shake
from~\S\ref{sec-implementation-bazel-cloud-shake}.
However, \Nix is not intended as a build system, and the coarse grained nature
(packages, not individual files) makes it targeted to a different purpose.
% John Ericson suggested in a blog comment that nix may be somewhat monadic, see:
% \url{https://blogs.ncl.ac.uk/andreymokhov/cloud-and-dynamic-builds/\#comment-1849}.

@@

%TODO: Add a reference to the paper about forall f. c f => (k -> f v) -> f a
\begin{minted}[xleftmargin=10pt]{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}
\noindent
provided we instantiate \hs{p} to something like
\hs{k}~\hs{->}~\hs{f}~\hs{v}~--~which many of the actual instances in that paper
do. The properties of such optics are well studied, and the functions like
\hs{dependencies} are very much based on observations from that field of work.
Alas, we have been unable to remove the \hs{Maybe} used to encode whether a file
is an input, without complicating other aspects of our definition. Furthermore,
the \hs{Build} abstraction lacks any further such symmetry.
